Energy and exergy analysis of a cruise ship

### 2017-07-19 Manuscript/Manuscript.tex
some updates.

\author[EPFL]{Francesco Baldi}
\author[Linneus]{Fredrik Ahlgren}
\author[DTU]{Tuong-Van Nguyen}
\author[CTU]{Cecilia Gabrielii}
\author[CTU]{Karin Andersson}

\address[EPFL]{Industrial Process Energy Systems Engineering (IPESE), \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, 1950, Sion, Switzerland}
\address[Linneus]{Kalmar Maritime Academy, Linnaeus University, Kalmar, Sweden}
\address[DTU]{Department of Mechanical Engineering, Technical University of Denmark, Lyngby, Denmark}
\address[CTU]{Department of Mechanics and Maritime Sciences, Chalmers University of technology, Gothenburg, Sweden}

@@

>>>>

\author[EPFL]{Francesco Baldi}
\author[Linnaeus]{Fredrik Ahlgren}
\author[DTU]{Tuong-Van Nguyen}
\author[CTU]{Cecilia Gabrielii}
\author[CTU]{Karin Andersson}

\address[EPFL]{Industrial Process Energy Systems Engineering (IPESE), \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne, 1950, Sion, Switzerland}
\address[Linnaeus]{Kalmar Maritime Academy, Linnaeus University, Kalmar, Sweden}
\address[DTU]{Department of Mechanical Engineering, Technical University of Denmark, Lyngby, Denmark}
\address[CTU]{Department of Mechanics and Maritime Sciences, Chalmers University of technology, Gothenburg, Sweden}

@@

All data-points were checked individually by creating a descriptive statistic and a histogram of each data-point. A filter was applied by setting up a pre-defined maximum and minimum value. As we do not know, or had any meaningful way of deriving, each individual sensors placement, sensor type or calibration status all data must be filtered and checked accordingly for outliers or bad data.
